Evaluation of 3-point correlation functions from structural images on CPU and GPU architectures: accounting for anisotropy effects

### 2024-02-12 paper.tex
Pfeile

\begin{figure*}[tp]
  \centering
  \includegraphics[width=0.6\linewidth]{images/workflow.png}
  \caption[]{A possible workflow for computation of correlation functions
    (clockwise from top left to bottom right ): 1.~rotating a sample in random
    directions (which is equivalent to rotating the sampling pattern),
    2.~calculating the correlation function for each direction, 3.~avegaring
    results across rotations, 4.~representing the result as a family of 2D
    plots. \highlight{Show "random rotation" at the slice, "Stack of directional
      functions" on the right-upper.}}
  \label{fig:workflow}
\end{figure*}

>>>>

\begin{figure*}[tp]
  \centering
  \includegraphics[width=0.6\linewidth]{images/workflow.png}
  \caption[]{A possible workflow for computation of correlation functions
    (clockwise from top left to bottom right ): 1.~rotating a sample in random
    directions (which is equivalent to rotating the sampling pattern),
    2.~calculating the correlation function for each direction, 3.~avegaring
    results across rotations, 4.~representing the result as a family of 2D
    plots.}
  \label{fig:workflow}
\end{figure*}
